---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # fig.path = "README-"
  fig.path = "tools/README-"
)
set.seed(0)
```

# bSMED

[![Travis-CI Build Status](https://travis-ci.org/CollinErickson/bSMED.svg?branch=master)](https://travis-ci.org/CollinErickson/bSMED)

This package implements the adaptive sampling algorithm from the
paper "Batch Sequential Minimum Energy Design with Design-Region Adaptation" by
Heeyoung Kim et al. (2017), published in Journal of Quality Technology Vol. 49,
No. 1, January 2017.

I have used the abbreviation `bSMED` to refer to this method. The main function provided by this package is the `bSMED` function, which creates an R6 object that performs the algorithm.

## Installation

You can install bSMED from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CollinErickson/bSMED")
```

## Example

See the vignette for a more in-depth description of the following example.

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code

# Get function
quad_peaks_slant <- TestFunctions::add_linear_terms(function(XX) {.2+.015*TestFunctions::add_zoom(TestFunctions::rastrigin, scale_low = c(.4,.4), scale_high = c(.6,.6))(XX)^.9}, coeffs = c(.02,.01))

# Create bSMED instance
a <- bSMED::bSMED$new(D=2,func=quad_peaks_slant,
                      obj="func", b=3, nb=5,
                      X0=lhs::maximinLHS(20,2),
                      Xopts=lhs::maximinLHS(500,2),
                      package="GauPro",
                      parallel=FALSE
                      )
a$run()
```
